\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-02 slides/gvn-hoist.tex
hoist
partition and cost models

@@

>>>>

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item DFS number all instructions
  \item Compute value number of scalars, loads, stores, calls
  \item Compute insertion points of each type of instructions
  \item Hoist expressions
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  \begin{itemize}
  \item Loads: value number the pointer operand
  \item Stores: value number the pointer operand and the value being stored
  \item Calls, Scalars: use the existing GVN infrastructure
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-compute insertion points}
 Insertion Point: A location where all the operands are either available
    or, can be made available.

  \begin{itemize}
  \item Compute a common insertion point for a set of instructions having the same GVN.
    (Similar to VBEs but not as strict)
  \item Partition the candidates into a smaller set of hoistable candidates when
    no common insertion points can be found (The instructions are sorted by their DFS numbers)
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-hoist expressions}
  \begin{itemize}
  \item Scalars: Just move one of the instrutions to the hoisting point and remove others. Update SSA.
  \item Loads and Stores: Try to make geps available (if not), and then hoist. Update SSA and memory SSA.
  \item Calls: Hoist just like scalars. Update SSA.
  \end{itemize}
}

@@

\frame{\frametitle{Cost models}
  \begin{itemize}
  \item Do not hoist too far
  \item Do not hoist GEPs
  \end{itemize}
}
